---
title: "Integrator test"
author: "Viacheslav Shalisko"
date: "22 of october 2017"
output: html_document
---


###  Parameters: MaxEnt model, high resolution predictors (7.5"), 4 presence points, 64 simulated presence points, random selection of 22-23 points, TGS with 2000 background ponts, evaluation with training and test AUV including ranking vs. null-models

```{r}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

## Data preparation
#### Set adjustable variables

```{r set-variables}
run_code <- '25'
basepath <- 'C:/Users/vshal/Downloads/R/'
basename <- 'Magnolia_mercedesiarum_MAXENT_HR_'
scriptpath <- 'C:/Users/vshal/OneDrive/Documentos_para_GD/Temp_Magnolia/test_run'

random_seed_folding <- 1
random_seed_background <- 1
random_background_number <- 100

presence_points_count <- 22

#layers_to_drop <- c(2,6,7,9,11,12,14,15,17,18,19)
layers_to_drop <- c(21)    # the last layer no. 21 is dummy (repetition of the first, included just to drop it)
```


#### Load modules

```{r load-modulos}
library(maptools)
library(rworldmap)    # worldmap datasets
library(rworldxtra)   # hires worldmap spatial dataframe

library(sp)
library(raster)
library(dismo)
library(rgdal)
library(rJava)

maxent.select.contribution <- function (m,n) {
  # parametros: m - objeto del model maxent, n - vector de nombres de variables raster
  resultados <- m@results
  tabla_resultados <- data.frame(t(rep(NA,3)))
  names(tabla_resultados) <- c('variable','contribution','permutation.importance')
  for (i in 1:length(n)) {
    variable1_name <- paste(n[i],'.contribution',sep='')
    variable1_value <- resultados[variable1_name,1]
    variable2_name <- paste(n[i],'.permutation.importance',sep='')
    variable2_value <- resultados[variable2_name,1]
    tabla_resultados <- rbind(tabla_resultados,c(n[i],variable1_value,variable2_value))
  }
  tabla_resultados <- tabla_resultados[-1,]
  return(tabla_resultados)
}


evaluate.mdl <- function (pnt,bkg,rast,mdl) {
  # pnt - presence points, bkg - background points, rast - raster dataset, mdl - model
  result <- list()
  values_bkg <- extract(rast, bkg)
  values_pnt <- extract(rast, pnt)
  values_pnt_bkg <- rbind(values_bkg, values_pnt)


  result$e <- evaluate(values_pnt, values_pnt_bkg, mdl)
  print(result$e)

  par(mfrow=c(2, 2))
  plot(result$e, 'TPR')
  plot(result$e, 'ROC')
  density(result$e)
  boxplot(result$e, col=c('lightblue','coral'), notch=TRUE)
  
  result$t <- threshold(result$e)
  print(result$t)
  
  result$v_bkg <- values_bkg
  result$v_pnt <- values_pnt
  
  return(result)
}

```

#### Load raster predictor variables

```{r load-rasters, cache=TRUE}

names <- c("alt","bio1","bio2","bio3","bio4",
              "bio5","bio6","bio7","bio8","bio9",
              "bio10","bio11","bio12","bio13","bio14",
              "bio15","bio16","bio17","bio18","bio19",
              "dummy")

#capas_raster<-stack("C:/Users/vshal/Downloads/Chelsea/Andes_HR/biovars_Andes_HR.tif")

capas_raster<-stack(c("C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_Andes.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_HR_mixed_T.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_HR_mixed_P.tif",
                      "C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_Andes.tif"))

capas_raster_small<-stack(c("C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_B500km.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_B500km_HR_mixed_T.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_B500km_HR_mixed_P.tif",
                      "C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_B500km.tif"))


names(capas_raster) <- names
names(capas_raster_small) <- names

capas_raster
capas_raster_small
#summary(capas_raster)

bio10 <- subset(capas_raster,10)
```

#### Load TGS raster

```{r load-tgs-raster, cache=TRUE, fig.height=8, fig.width=12}
# load raster of TGS mask in full extent
tgs_raster_full <- stack("C:/Users/vshal/Downloads/GBif/GBif_magnoliopsida_KD_Andes_5km_2only.tif")
# load raster of TGS mask buffered with 500 km
tgs_raster_500 <- stack("C:/Users/vshal/Downloads/GBif/GBif_magnoliopsida_KD_Andes_5km_2only_MM_B500.tif")
# load raster of TGS mask buffered with 750 km
tgs_raster_750 <- stack("C:/Users/vshal/Downloads/GBif/GBif_magnoliopsida_KD_Andes_5km_2only_MM_B750.tif")

tgs_raster_full
tgs_raster_750
tgs_raster_500

par(mfrow=c(1, 3))
world_high <- getMap(resolution = "high")

plot(tgs_raster_500, main="TGS 500 km", legend=FALSE)
#plot(tgs_raster_500, legend.only=TRUE)
plot(world_high, add=TRUE)

plot(tgs_raster_750, main="TGS 750 km", legend=FALSE)
plot(world_high, add=TRUE)

plot(tgs_raster_full, main="TGS full extent", legend=FALSE)
plot(world_high, add=TRUE)

```


#### Load presence data: 1) main dataset, 2) additional fixed control dataset

```{r load-presence-data}
# load main presence dataset
puntos_entrenamiento<- read.csv("C:/Users/vshal/OneDrive/Documentos_para_GD/Temp_Magnolia/Magnolia_mercedesiarum_extra.csv")
dim(puntos_entrenamiento)
head(puntos_entrenamiento)
tail(puntos_entrenamiento)

#attach(puntos_entrenamiento)
puntos_entrenamiento_coordenadas_preliminar<-data.frame(cbind(
                              puntos_entrenamiento[,'Lon'],
                              puntos_entrenamiento[,'Lat']))



# load additional fixed control points
puntos_control<- read.csv("C:/Users/vshal/OneDrive/Documentos_para_GD/Temp_Magnolia/Magnolia_mercedesiarum.csv")
dim(puntos_control)
head(puntos_control)
tail(puntos_control)

#attach(puntos_control)
puntos_control_coordenadas<-data.frame(cbind(
                            puntos_control[,'Lon'],
                            puntos_control[,'Lat']))
```

#### Cross-validated SDM

```{r integrator}
iterations <- list()

for (i in 1:10){
  random_seed_folding <- i
  random_seed_background <- i
  
  rmarkdown::render('C:/Users/vshal/OneDrive/Documentos_para_GD/Temp_Magnolia/test_run/renderer.Rmd', 
                   output_file =  paste("step_", run_code, '_', i, ".html", sep=''), 
                   output_dir = scriptpath)
}
```

```{r cross-validation-output}

#str(iterations)

saveRDS(iterations, paste(scriptpath, "/iterations_object_",run_code,".rds",sep=""))


```




