---
title: "Predictor test"
author: "Viacheslav Shalisko"
date: "12 of november 2017"
output: html_document
---


###  Parameters: MaxEnt model, high resolution predictors (7.5"), 4 presence points, 64 simulated presence points, random selection of 22-23 points, TGS with 2000 background ponts, evaluation with training and test AUV including ranking vs. null-models

```{r}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

## Data preparation
#### Set adjustable variables

```{r set-variables}
run_code <- '25'
basepath <- 'C:/Users/vshal/Downloads/R/'
basename <- 'Magnolia_mercedesiarum_MAXENT_HR_'
scriptpath <- 'C:/Users/vshal/OneDrive/Documentos_para_GD/Temp_Magnolia/test_run'

random_seed_folding <- 1
random_seed_background <- 1
random_background_number <- 100

presence_points_count <- 22

#layers_to_drop <- c(2,6,7,9,11,12,14,15,17,18,19)
layers_to_drop <- c(21)    # the last layer no. 21 is dummy (repetition of the first, included just to drop it)
```


#### Load modules

```{r load-modulos}
library(maptools)
library(rworldmap)    # worldmap datasets
library(rworldxtra)   # hires worldmap spatial dataframe

library(sp)
library(raster)
library(dismo)
library(rgdal)
library(rJava)


```

#### Load raster predictor variables

```{r load-rasters, cache=TRUE}

names <- c("alt","bio1","bio2","bio3","bio4",
              "bio5","bio6","bio7","bio8","bio9",
              "bio10","bio11","bio12","bio13","bio14",
              "bio15","bio16","bio17","bio18","bio19",
              "dummy")

#capas_raster<-stack("C:/Users/vshal/Downloads/Chelsea/Andes_HR/biovars_Andes_HR.tif")

capas_raster<-stack(c("C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_Andes.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_HR_mixed_T.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_HR_mixed_P.tif",
                      "C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_Andes.tif"))

capas_raster_small<-stack(c("C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_B500km.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_B500km_HR_mixed_T.tif",
                      "C:/Users/vshal/Downloads/Chelsea/biovar_Andes_B500km_HR_mixed_P.tif",
                      "C:/Users/vshal/Downloads/GMTED2010/GMTED2010_075_B500km.tif"))


names(capas_raster) <- names
names(capas_raster_small) <- names

capas_raster
capas_raster_small
#summary(capas_raster)

bio10 <- subset(capas_raster,10)
```

#### Drop unsignificant layers (based on preliminary test run)

```{r drop-layers}
capas_raster_drop <- dropLayer(capas_raster,layers_to_drop)
capas_raster_small_drop <- dropLayer(capas_raster_small,layers_to_drop)
names_after_drop <- names(capas_raster_drop)
```


```{r cross-validation-load}
iterations <- readRDS(paste(scriptpath, "/iterations_object_",run_code,".rds",sep=""))

#str(iterations)
```

## Prediction
#### Predict presence probaility surface

```{r apply-model, fig.height=16, fig.width=10}
cross_validation_lenght <- 10

for (j in 1:cross_validation_lenght) {
  my_obj <- iterations[[j]]
  resultado_maxent <- predict(my_obj$model, capas_raster_small_drop, 
                           na.rm=TRUE,
                           progress = 'windows') 
  
  writeRaster(resultado_maxent, filename=paste(basepath, basename ,'run_',run_code,'_',j,'.tif',sep=''), 
           format="GTiff", overwrite=TRUE)
  
  plot(resultado_maxent, main = paste('probability raster ',j,sep=''))
  #plot(bio10, xlim=c(-82,-70), ylim=c(-10,10), axes=TRUE)
  world_high <- getMap(resolution = "high")
  #plot(world_high, xlim=c(-82,-70), ylim=c(-10,10), axes=TRUE)
  plot(world_high, add=TRUE)
  
  puntos_entrenamiento_coordenadas<-data.frame(cbind(
                              my_obj$entr$X1,
                              my_obj$entr$X2))  
  
  points(puntos_entrenamiento_coordenadas, col='red')
  #str(my_obj)
  #str(my_obj$auc_null_model_mean)

  #plot(my_obj$e_train$e, 'ROC')
  #print(my_obj$e_train)
  #iterations[j]$e_train$e@auc
  
}


```



